---
title: "Modeling and prediction for movies"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(statsr)
```

### Load data

```{r load-data}
load("movies.Rdata")
```



* * *

## Part 1: Data


* * *

## Part 2: Research question

My research question concerns understanding how movie rating scores are related to movie awards, movie length, and title type (feature vs. documentary). I am interested in whether critics and audiences share similar regression models for predicting rating scores, respectively. 



* * *

## Part 3: Exploratory data analysis


```{r}
movies2 <- filter(movies, title_type == "Documentary" | title_type == "Feature Film")



```


* * *

## Part 4: Modeling

```{r}
summary(lm(movies2, formula = audience_score ~ best_pic_nom + best_pic_win +
             best_actress_win + best_actor_win + best_dir_win +
             title_type + runtime))

summary(lm(movies2, formula = critics_score ~ best_pic_nom + best_pic_win +
             best_actress_win + best_actor_win + best_dir_win +
             title_type + runtime))

```


* * *

## Part 5: Prediction

```{r}

```


* * *

## Part 6: Conclusion

